A Study on Online Sequential Learning using Bandits

### 2017-12-11 synopsis/intro.tex
Latest on 10/12/2017
Latest on 11/12/2017

\begin{figure}[!th]
\includegraphics[scale=0.45]{synopsis/img/RL1.png}
\caption{Reinforcement Learning}
\label{fig:rl}
\end{figure}

@@

	The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observes the reward associated with that arm which is sampled from a distribution associated with the specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit.

>>>>

\begin{figure}[!th]
\begin{center}
\includegraphics[scale=0.3]{synopsis/img/RL1.png}
\caption{Reinforcement Learning}
\label{fig:rl}
\end{center}
\end{figure}

@@

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm which is sampled from a distribution associated with the specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit.
